Calendar-based graphics for visualizing people's daily schedules

### 2017-08-04 main.Rmd
done with captions

(ref:facet-time-cap) Hourly pedestrian counts faceted by sensors and days of the week using lines. It features at least two types of seasons---time of day and day of week---across all the sensors.

@@

(ref:month-diagram-cap) Illustration of the indexing layout for cells in a month.

@@

(ref:year-diagram-cap) Illustration of the indexing layout for months of one year.

@@

(ref:boxplot-cap) Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing loess smooth line for each day. It shows the hourly distribution in the city as a whole. There is one sensor attracting a larger number of people on New Year's Eve than the rest.

@@

(ref:chn-cap) The same side-by-side boxplot as Figure \ref{fig:boxplot}, but with the month and week day labels in Chinese. It demonstrates the natural support for languages other than English.

@@

>>>>

(ref:facet-time-cap) Hourly pedestrian counts for 2016 faceted by sensors and days of the week using lines. It features at least two types of seasons---time of day and day of week---across all the sensors. The white night effect increasing pedestrian counts can be seen on Saturday in February at State Library.

@@

(ref:month-diagram-cap) Illustration of the indexing layout for cells in a month. $k$ is day of the week, $g$ is day of the month, $i,j$ indicates grid position.

@@

(ref:year-diagram-cap) Illustration of the indexing layout for months of one year. $M,N$ indicate number of rows and columns, $b$ is a space parameter separating cells.

@@

(ref:boxplot-cap) Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. There is one sensor attracting a larger number of people on New Year's Eve than the rest.

@@

(ref:chn-cap) The same plot as Figure \ref{fig:boxplot}, but with the month and week day labels in Chinese. It demonstrates the natural support for languages other than English.

@@

The focus is on the western calendar layout because most countries have adopted this format. However the language of labels would differ across countries, and so support was added for changing the label language simply.

### 2017-08-04 main.tex
done with captions

\caption[Hourly pedestrian counts faceted by sensors and
days of the week using lines. It features at least two types of
seasons---time of day and day of week---across all the sensors.]{Hourly pedestrian counts faceted by sensors and
days of the week using lines. It features at least two types of
seasons---time of day and day of week---across all the sensors.}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for cells in
a month.]{Illustration of the indexing layout for cells in
a month.}\label{fig:month-diagram}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for months of
one year.]{Illustration of the indexing layout for months of
one year.}\label{fig:year-diagram}
\end{figure}
\end{CodeChunk}

@@

\caption[Side-by-side boxplot of hourly counts across all the
43 sensors in December of 2016, with the superimposing loess smooth line
for each day. It shows the hourly distribution in the city as a whole.
There is one sensor attracting a larger number of people on New Year's
Eve than the rest.]{Side-by-side boxplot of hourly counts across all the
43 sensors in December of 2016, with the superimposing loess smooth line
for each day. It shows the hourly distribution in the city as a whole.
There is one sensor attracting a larger number of people on New Year's
Eve than the rest.}\label{fig:boxplot}
\end{figure}
\end{CodeChunk}

@@

\caption[The same side-by-side boxplot as Figure \ref{fig:boxplot},
but with the month and week day labels in Chinese. It demonstrates the
natural support for languages other than English.]{The same side-by-side boxplot as Figure \ref{fig:boxplot},
but with the month and week day labels in Chinese. It demonstrates the
natural support for languages other than English.}\label{fig:chn}
\end{figure}
\end{CodeChunk}

>>>>

\caption[Hourly pedestrian counts for 2016 faceted by
sensors and days of the week using lines. It features at least two types
of seasons---time of day and day of week---across all the sensors. The
white night effect increasing pedestrian counts can be seen on Saturday
in February at State Library.]{Hourly pedestrian counts for 2016 faceted by
sensors and days of the week using lines. It features at least two types
of seasons---time of day and day of week---across all the sensors. The
white night effect increasing pedestrian counts can be seen on Saturday
in February at State Library.}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for cells in
a month. \(k\) is day of the week, \(g\) is day of the month, \(i,j\)
indicates grid position.]{Illustration of the indexing layout for cells in
a month. \(k\) is day of the week, \(g\) is day of the month, \(i,j\)
indicates grid position.}\label{fig:month-diagram}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for months of
one year. \(M,N\) indicate number of rows and columns, \(b\) is a space
parameter separating cells.]{Illustration of the indexing layout for months of
one year. \(M,N\) indicate number of rows and columns, \(b\) is a space
parameter separating cells.}\label{fig:year-diagram}
\end{figure}
\end{CodeChunk}

@@

\caption[Side-by-side boxplots of hourly counts for all the 43
sensors in December 2016, with the loess smooth line superimposed on
each day. It shows the hourly distribution in the city as a whole. There
is one sensor attracting a larger number of people on New Year's Eve
than the rest.]{Side-by-side boxplots of hourly counts for all the 43
sensors in December 2016, with the loess smooth line superimposed on
each day. It shows the hourly distribution in the city as a whole. There
is one sensor attracting a larger number of people on New Year's Eve
than the rest.}\label{fig:boxplot}
\end{figure}
\end{CodeChunk}

@@

\caption[The same plot as Figure \ref{fig:boxplot}, but with the
month and week day labels in Chinese. It demonstrates the natural
support for languages other than English.]{The same plot as Figure \ref{fig:boxplot}, but with the
month and week day labels in Chinese. It demonstrates the natural
support for languages other than English.}\label{fig:chn}
\end{figure}
\end{CodeChunk}
